Constraining tensorial and scalar couplings with $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-06-26 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] added missing numbers to table for TT5 scenario

\preprint{EOS-2014-??, FLAVOUR(267104)-ERC-??}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  \hline \hline
  $\mbox{Re}\,\wilson{T}$
  & $\quad$ $[-0.32,\, 0.16]$ ($[-0.52,\, 0.35]$) $\quad$
  & \eos{$\quad$ $[-0.19,\, 0.13]$ ($[-0.34,\, 0.27]$) $\quad$}
  & $\quad$ $[-0.23,\, 0.14]$ ($[-0.39,\, 0.30]$) $\quad$
  \\
  $\mbox{Im}\,\wilson{T}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & \eos{$[-0.16,\, 0.17]$ ($[-0.31,\, 0.31]$)}
  & $[-0.17,\, 0.22]$ ($[-0.33,\, 0.37]$)
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & \eos{$[-0.07,\, 0.25]$ ($[-0.23,\, 0.38]$)}
  & $[-0.18,\, 0.16]$ ($[-0.32,\, 0.32]$)
  \\
  $\mbox{Im}\,\wilson{T5}$
  & $[-0.24,\, 0.25]$ ($[-0.44,\, 0.45]$)
  & \eos{$[-0.17,\, 0.16]$ ($[-0.31,\, 0.31]$)}
  & $[-0.20,\, 0.18]$ ($[-0.36,\, 0.35]$)
  \\
  \hline
  $|\wilson{T}|$, $|\wilson{T5}|$
  & $[0.13,\, 0.43]$ ($[0.03,\, 0.57]$)
  & \eos{$< 0.25$ ($< 0.35$)}
  & $[0.10,\, 0.33]$ ($[0.02,\, 0.43]$)
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cTT5:1-dimCLs}
     The constraints on complex-valued $\wilson{T,\,T5}$ --- [upper] 1D-marginalized
     at 68\% (95\%) probability and [lower] 2D-marginalized --- when using
     measurements of $i)$ only $F_H^\mu$, $ii)$ $F_H^\mu$ and other data in
     \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and $iii)$ allowing
     also complex-valud new physics contributions to $\wilson{9,\,10}$.
  }
\end{table*}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.5}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{cc|c|ccc}
  \hline
    observable
  & $q^2$-bin [GeV$^2$]
  & SM
  & $9,10,T,T5$
  & $10^{(')},S^{(')},P^{(')}$
  & $10^{(')},S^{(')},P^{(')},T,T5$
  \\
  \hline \hline
  \multirow{2}{*}{$J_{6c}$}
  & $[1.1,\, 6]$
  & $\simeq 0$
  & \eos{$(-1.27_{-0.64}^{+3.08}) \cdot 10^{-21}$}
  & \eos{$( 0.01_{-0.12}^{+0.06}) \cdot 10^{-21}$}
  & \eos{$( 0.71_{-1.98}^{+0.52}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & $\simeq 0$
  & \eos{$(-0.43_{-0.25}^{+1.06}) \cdot 10^{-21}$}
  & \eos{$(-0.03_{-0.00}^{+0.02}) \cdot 10^{-21}$}
  & \eos{$(-0.25_{-0.23}^{+0.72}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$J_{1c} + J_{2c}$}
  & $[1.1,\, 6]$
  & \eos{$(1.80_{-0.26}^{+0.30}) \cdot 10^{-21}$}
  & \eos{$(3.05_{-0.96}^{+1.31}) \cdot 10^{-21}$}
  & \eos{$(1.22_{-0.17}^{+0.26}) \cdot 10^{-21}$}
  & \eos{$(3.23_{-1.31}^{+2.36}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & \eos{$(8.75_{-1.82}^{+2.05}) \cdot 10^{-23}$}
  & \eos{$(5.63_{-2.58}^{+3.29}) \cdot 10^{-21}$}
  & \eos{$(7.49_{-2.02}^{+1.01}) \cdot 10^{-23}$}
  & \eos{$(7.28_{-3.29}^{+5.17}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$J_{1s} - 3 J_{2s}$}
  & $[1.1,\, 6]$
  & \eos{$(2.04_{-0.50}^{+0.57}) \cdot 10^{-22}$}
  & \eos{$(1.46_{-0.60}^{+0.76}) \cdot 10^{-20}$}
  & \eos{SM}
  & \eos{$(2.00_{-0.97}^{+1.03}) \cdot 10^{-20}$}
  \\
  & $[15,\, 19]$
  & \eos{$(5.99_{-1.08}^{+1.19}) \cdot 10^{-23}$}
  & \eos{$(6.57_{-2.72}^{+3.40}) \cdot 10^{-21}$}
  & \eos{SM}
  & \eos{$(9.29_{-4.54}^{+3.86}) \cdot 10^{-21}$}
  \\
  \hline \hline
  \multicolumn{2}{c|}{$A_{\Delta \Gamma}$}
  & 1
  &
  & SM
  &
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:postdictions}
     The 68\% probability intervals of not yet measured angular observables in
     $B^0\to K^{*0}\bar\mu\mu$ integrated over $q^2$ bins at low- and high-$q^2$ 
     for several new physics scenarios respecting all the considered experimental
     constraints. The SM prediction with respective
     uncertainties are given too, where ``$\simeq 0$'' indicates zero in the considered
     approximation, see text for more explanations.
  }
\end{table*}

>>>>

\preprint{EOS-2015-??, FLAVOUR(267104)-ERC-??}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  \hline \hline
  $\mbox{Re}\,\wilson{T}$
  & $\quad$ $[-0.32,\, 0.16]$ ($[-0.52,\, 0.35]$) $\quad$
  & $\quad$ $[-0.29,\, 0.09]$ ($[-0.43,\, 0.27]$) $\quad$
  & $\quad$ $[-0.23,\, 0.14]$ ($[-0.39,\, 0.30]$) $\quad$
  \\
  $\mbox{Im}\,\wilson{T}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & $[-0.19,\, 0.21]$ ($[-0.37,\, 0.35]$)
  & $[-0.17,\, 0.22]$ ($[-0.33,\, 0.37]$)
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & $[-0.19,\, 0.17]$ ($[-0.33,\, 0.33]$)
  & $[-0.18,\, 0.16]$ ($[-0.32,\, 0.32]$)
  \\
  $\mbox{Im}\,\wilson{T5}$
  & $[-0.24,\, 0.25]$ ($[-0.44,\, 0.45]$)
  & $[-0.21,\, 0.19]$ ($[-0.37,\, 0.35]$)
  & $[-0.20,\, 0.18]$ ($[-0.36,\, 0.35]$)
  \\
  \hline
  $|\wilson{T}|$, $|\wilson{T5}|$
  & $[0.13,\, 0.43]$ ($[0.03,\, 0.57]$)
  & $[0.09,\, 0.33]$ ($[0.02,\, 0.44]$)
  & $[0.10,\, 0.33]$ ($[0.02,\, 0.43]$)
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cTT5:1-dimCLs}
     The constraints on complex-valued $\wilson{T,\,T5}$ --- [upper] 1D-marginalized
     at 68\% (95\%) probability and [lower] 2D-marginalized --- when using
     measurements of $i)$ only $F_H^\mu$, $ii)$ $F_H^\mu$ and other data in
     \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and $iii)$ allowing
     also complex-valud new physics contributions to $\wilson{9,\,10}$.
  }
\end{table*}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.5}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{cc|c|ccc}
  \hline
    observable
  & $q^2$-bin [GeV$^2$]
  & SM
  & $9,10,T,T5$
  & $10^{(')},S^{(')},P^{(')}$
  & $10^{(')},S^{(')},P^{(')},T,T5$
  \\
  \hline \hline
  \multirow{2}{*}{$J_{6c}$}
  & $[1.1,\, 6]$
  & $\simeq 0$
  & \eos{$(-1.27_{-0.64}^{+3.08}) \cdot 10^{-21}$}
  & \eos{$( 0.01_{-0.12}^{+0.06}) \cdot 10^{-21}$}
  & \eos{$( 0.71_{-1.98}^{+0.52}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & $\simeq 0$
  & \eos{$(-0.43_{-0.25}^{+1.06}) \cdot 10^{-21}$}
  & \eos{$(-0.03_{-0.00}^{+0.02}) \cdot 10^{-21}$}
  & \eos{$(-0.25_{-0.23}^{+0.72}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$J_{1c} + J_{2c}$}
  & $[1.1,\, 6]$
  & \eos{$(1.80_{-0.26}^{+0.30}) \cdot 10^{-21}$}
  & \eos{$(3.05_{-0.96}^{+1.31}) \cdot 10^{-21}$}
  & \eos{$(1.22_{-0.17}^{+0.26}) \cdot 10^{-21}$}
  & \eos{$(3.23_{-1.31}^{+2.36}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & \eos{$(8.75_{-1.82}^{+2.05}) \cdot 10^{-23}$}
  & \eos{$(5.63_{-2.58}^{+3.29}) \cdot 10^{-21}$}
  & \eos{$(7.49_{-2.02}^{+1.01}) \cdot 10^{-23}$}
  & \eos{$(7.28_{-3.29}^{+5.17}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$J_{1s} - 3 J_{2s}$}
  & $[1.1,\, 6]$
  & \eos{$(2.04_{-0.50}^{+0.57}) \cdot 10^{-22}$}
  & \eos{$(1.46_{-0.60}^{+0.76}) \cdot 10^{-20}$}
  & \eos{SM}
  & \eos{$(2.00_{-0.97}^{+1.03}) \cdot 10^{-20}$}
  \\
  & $[15,\, 19]$
  & \eos{$(5.99_{-1.08}^{+1.19}) \cdot 10^{-23}$}
  & \eos{$(6.57_{-2.72}^{+3.40}) \cdot 10^{-21}$}
  & \eos{SM}
  & \eos{$(9.29_{-4.54}^{+3.86}) \cdot 10^{-21}$}
  \\
  \hline \hline
  \multicolumn{2}{c|}{$A_{\Delta \Gamma}$}
  & 1
  &
  & SM
  &
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:postdictions}
     The 68\% probability intervals of not yet measured angular observables in
     $B^0\to K^{*0}\bar\mu\mu$ integrated over $q^2$ bins at low- and high-$q^2$ 
     for several new physics scenarios respecting all the considered experimental
     constraints. The SM prior predictives are given too, where ``$\simeq 0$'' 
     indicates zero in the considered
     approximation, see text for more explanations.
  }
\end{table*}
